Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
pass on lessons learned

\begin{center}
  \fbox{
    \begin{minipage}{8cm}
      \textit{Summary:}~Cross-engine differential testing was also
      effective at finding several bugs in \js\ engines. However,
      relative to test transplantation, it required substantial more
      human effort, which may play a lesser role with improved
      automation.
      \end{minipage}
    }
\end{center}

@@

\subsection{Lessons}

For example, a test that passes in one engine could
legitimately fail in a different engine because of some undefined
behavior in the spec. The most recent
\js\ specification~\cite{ecmas262-spec} documents several of these
cases, which can be traced looking for the string ``implementation-dependent''. As another example, a test
may fail because the engine does not fully implement some feature. The
publicly-available Kangax compatibility table~\cite{kangax} relates
\js\ features with the engines that support them. To sum, it is often
non-trivial to assess if a test fails because of a bug or because of
some other reason making test automation more challenging.

\Fix{...}

% \subsection{LO bugs}
% 
% \Igor{For example, a bug caught by our environment and reported as LO priority was reported 
% on \chakra{} engine, the JS code can be found in Figure~\ref{fig:lo-priority}. In this case,
% this is a seed from Mozilla suite (\CodeIn{mozilla/non262/statements/for-in-with-assignments.js}),
% the warning was not caught by the \CodeIn{assertEq} function that compares if two arguments are equals, 
% the bug appears inside the generator function\footnote{Generators \url{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Statements/function*}}
% at line 2. According to ES6 specification\footnote{ES6 YieldExpression \url{https://www.ecma-international.org/ecma-262/8.0/index.html\#prod-YieldExpression}},
% it is allowed the use of \CodeIn{yield in} in a \CodeIn{for} loop. In our infrastructure,
% only \chakra{} engine fails with an error output \CodeIn{SyntaxError: Syntax error}, due
% the output does not shows nothing related with assertions, we considered this one as a warning from LO group.
% Until now, the issue was confirmed and waiting for merge/closed.
% \Fix{checar ate o prazo de submissao. Essa issue esta confirmada e com commits, falta apenas o merge.}
% }
% \begin{figure}[h!]
%   \centering
%   \scriptsize
%   \lstset{escapeinside={@}{@},
%     numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
%     basicstyle=\ttfamily\scriptsize, boxpos=c,
%     numberstyle=\tiny,
%     morekeywords={assertEq, var, yield, in, function},
%   }
%   \begin{lstlisting}
% function* g1() {
%   for (var x = yield in {}) ;
% }
% var it = g1();
% assertEq(it.next().done, false);
% assertEq(it.next().done, true);
%   \end{lstlisting}
%   \normalsize
%   \caption{Bug caught by our environment as LO priority.}
%   \label{fig:lo-priority}
%   \end{figure}

>>>>

\begin{center}
  \fbox{
    \begin{minipage}{8cm}
      \textit{Summary:}~Cross-engine differential testing was also
      effective at finding bugs in \js\ engines. However, compared to
      test transplantation, it required substantial more human effort
      per bug found.
      \end{minipage}
    }
\end{center}

@@

\subsection{Lessons Learned}

We learned several lessons in this study:

\begin{itemize}
  \item The diversity-aware techniques we used in this study are great
    at finding bugs in \js\ engines;
  \item The cost of inpecting failures/warnings is high. Although the
    inspection activity was not uninterrupted, it is safe to say that
    each warning required a substantial amount of time to analyze for
    potential false alarms;
  \item Even simple black-box fuzzers can create surprisingly
    interesting inputs;
  \item Mozilla's \smonkey\ appears to be the most reliable
    \js\ engine, with Google's \veight\ after it;
  \item Reporting real bugs is a great way to train (and encourage)
    students in software testing.
\end{itemize}
